---
title: "LidR Notebook"
---

#import library

The installation of the package "EBImage" is bit tricky:

https://github.com/aoles/EBImage
Tried:   install.packages("BiocManager")
Error:   package BiocManager is not available (for R version 3.4.4)

https://stackoverflow.com/questions/37222603/i-want-to-use-ebimage-package-but-it-says-it-is-not-available-for-my-version-o
Tried:    source("http://bioconductor.org/biocLite.R")
Error:    compilation failed for package ‘fftwtools’
          * removing‘/home/klk/R/x86_64-pc-linux-gnu-library/3.4/fftwtools’

https://github.com/GuangchuangYu/ggtree/wiki/ggtree-installation 
Tried:    On Ubuntu 16.04.1 LTS, you need to install:
          sudo apt-get install libfftw3-3 libfftw3-dev libtiff5-dev

Again Tried: source("http://bioconductor.org/biocLite.R")
Message:  Bioconductor version 3.6 (BiocInstaller 1.28.0), ?biocLite for help. A new version of Bioconductor is available after installing the most recent version of R; see http://bioconductor.org/install

Tried:    biocLite("EBImage")
Message:  
The downloaded source packages are in ‘/tmp/RtmppMRvER/downloaded_packages’ installation path not writeable, unable to update packages: codetools, foreign, lattice, spatial Old packages: 'callr', 'cli', 'commonmark', 'covr', 'data.table', 'digest', 'evaluate', 'fansi', 'htmlwidgets', 'later', 'link2GI', 'maptools', 'mapview', 'microbenchmark', 'mime', 'packcircles', 'pkgbuild', 'pkgload', 'R6', 'Rcpp', 'reprex', 'rgrass7', 'rstudioapi', 'spatstat.data', 'spatstat.utils', 'spData', 'testthat', 'tidyselect', 'tinytex', 'tweenr', 'units', 'webshot', 'xtable', 'xts', 'zoo' Update all/some/none? [a/s/n]:

https://support.bioconductor.org/p/92247/
https://support.bioconductor.org/p/111316/
https://stackoverflow.com/questions/28546382/installed-directory-not-writable-cannot-update-packages-boot-class-kerns

Terminal: 
Tried:    sudo R
          source("http://bioconductor.org/biocLite.R")
          biocLite("EBImage")
Message:  
The downloaded source packages are in ‘/tmp/RtmpblDrPJ/downloaded_packages’ Old packages: 'callr', 'cli', 'commonmark', 'covr', 'data.table', 'digest', 'evaluate', 'fansi', 'htmlwidgets', 'later', 'link2GI', 'maptools','mapview', 'microbenchmark', 'mime', 'packcircles', 'pkgbuild', 'pkgload','R6', 'Rcpp', 'reprex', 'rgrass7', 'rstudioapi', 'spatstat.data' 'spatstat.utils', 'spData', 'testthat', 'tidyselect', 'tinytex', 'tweenr','units', 'webshot', 'xtable', 'xts', 'zoo', 'codetools', 'foreign','lattice', 'spatial' Update all/some/none? [a/s/n]: n

Tried: install.packages("EBImage")

```{r}

library(lidR)
library(raster)
library(sf)
library("RColorBrewer")
#library("EBImage", lib.loc="C:/Program Files/R/R-3.4.2/library")

```

# import data

```{r}

las <- readLAS("/home/klk/Desktop/Stat/LidR/Data_in/26805_12475.laz")
baumkataster <- st_read("/home/klk/Desktop/Data/Baumkataster/Baumkataster.shp")

```

# View data

```{r}

View(las)

las@data
las@header
las@crs

# look at the data in more detail
las@data
las@data$X
sort(unique(las@data$Classification))

```

# plot data

```{r}

# colour visualizes the height
plot(las)

# colour visualizes the classifciation
col = c("red", "orange", "yellow", "lawngreen", "limegreen" ,"cyan","blue", "deeppink", "saddlebrown", "darkviolet", "white", "grey","black")
plot(las, color = "Classification", colorPalette  = col)

```

# subset data

```{r}

# subset data based on classification
las_5 <- las@data[which(las@data$Classification %in% c(5)),]
plot(LAS(las_5))

# subset dat based on height
sort(las@data$Z, decreasing = TRUE)
max(las@data$Z)
min(las@data$Z)

las_s600 <- las@data[which(las@data$Z < 600),]
plot(LAS(las_s600 ))
plot(LAS(las_s600 ), color = "Classification", colorPalette  = col)

```

# tree segmentation

```{r}

# Compute a canopy height model
# https://github.com/Jean-Romain/lidR
th = c(0,2,5,10,15)
edge = c(0, 1.5)
chm = grid_tincanopy(LAS(las_5), thresholds = th, max_edge = edge) 
plot(chm)
chm = as.raster(chm)
raster::plot(chm, col = height.colors(50)) 

# Segment the trees
# see: https://github.com/Jean-Romain/lidR/wiki/Tree-segmentation-from-A-to-Z
lastrees(LAS(las_5), "watershed", chm, th = 4)
tree = lasfilter(LAS(las_5), !is.na(treeID)) # remove points that are not assigned to 
plot(tree, color = "treeID", colorPalette = pastel.colors(100))
tree@data
length(unique(tree@data$treeID))

# return extra output from lastrees
# see: https://github.com/Jean-Romain/lidR/wiki/Tree-segmentation-from-A-to-Z
crowns = lastrees(LAS(las_5), "watershed", chm, th = 4, extra = TRUE)
contour = rasterToPolygons(crowns, dissolve = TRUE)
contour_sf= st_as_sf(contour, "sf")
centroid <- st_centroid(contour_sf)

# plot results
# see: https://github.com/Jean-Romain/lidR/wiki/Tree-segmentation-from-A-to-Z
plot(chm, col = height.colors(50))
plot(contour, add = T)
plot(centroid, add = T, pch= 19, col = "red", cex = 0.1)

plot(LAS(las_5))

```

